\section{Architecture: Minimal Changes to the Vehicle}
\label{sec:architecture}

If minimal fleets are the deployment model, the per-vehicle cost of joining one must be small, so we state the architecture as a bill of changes: what is added to an existing car, and what is not touched. Four functions are added, sensing, an ego-centric digital twin, a learned advisory policy, and a safety and etiquette filter, plus a display. Nothing else changes. There is no connection to throttle, brake, steering, or the CAN control plane; the OBD-II port, present on every car sold in the US since 1996, is read only, supplying ego speed; no persistent identity leaves the vehicle; and no backend sits in the real-time loop. Offline training may use centralized data and simulation, but the runtime loop stays on the vehicle, and the kit installs like a dashcam.

\noindent\textbf{Sensing and fusion.}
Each vehicle estimates its immediate scene from onboard sensors: ego speed, acceleration, lane, headway, leader and follower gaps, relative speeds, local density, queue estimate, and distance to a merge. Aggregate summaries, when heard, add peer-derived state over a bounded radius. The combined observation is deliberately not a global state but an ego-local one, with a few semantic hints about what lies outside direct perception. The deployment stack mirrors the simulator's observation contract rather than inventing a separate API, in our prototype a 39-field observation vector vendored verbatim from the training code and covered by bit-equality tests, and logs every field with provenance (measured, derived, fallback-neutral, static, or sim-parity). Ego speed, for instance, is measured from GPS, held during short dropouts, and can be cross-checked against on-vehicle odometry. Leader gap and closing speed come from forward tracks, density from forward counts, rear-lane fields from neutral fallbacks until a rear camera is added, and nearby-vehicle fields from peer summaries when enabled. That provenance map doubles as an observation-quality signal for both the policy and the safety layer.

\noindent\textbf{The ego-centric digital twin.}
At runtime, each vehicle maintains a lightweight, continuously updated model of its local road state: the ego vehicle, nearby vehicles, lane structure, merge pressure, and short-horizon congestion risk. This is the digital twin. It is a compact tracker, not a city-scale simulator running in the car, and its job is observability. It lets the controller reason about partially observed density and downstream pressure instead of reacting only to the closest leader, and it lets the safety layer test an advisory against a short-horizon prediction before it is shown. The twin also records when each aggregate was last refreshed and from which source; this is what lets the policy distinguish ``I see no cooperating vehicles'' from ``the radio is stale'', and lets the safety layer reject advisories that depend on low-confidence state.

\noindent\textbf{Centralized training, decentralized execution.}
The learning structure is centralized training with decentralized execution (CTDE). During training, a simulator or a logged fleet can expose global state and counterfactual rollouts; during execution, the policy receives only onboard sensing and local aggregate fields, so no coordinator enters the runtime dependency chain. This split is the technical bridge from the centralized predecessor~\cite{self_regulating_cars} to a vehicle-native system. Because a deployed policy must meet unseen merge geometries, demand patterns, and compliance levels, we view model-based reinforcement learning, learning a dynamics model of the road network and adapting the policy within it, as the most promising route to cross-topology adaptation at acceptable sample cost~\cite{sutton1991dyna,janner2019trust,hafner2020dream}.

\noindent\textbf{Advisory control.}
The action space stays conservative: speed bins, headway targets, and cautious lane preferences rather than raw throttle, braking, or aggressive lane-change commands. The public action has four fields: a speed bin ('slow', 'nominal', 'fast'), a headway bin, a cautious lane preference, and a merge mode. Prior work on self-regulating cars shows that discrete speed and headway bins of this kind are sufficient for a learned policy to improve flow and reduce hard braking~\cite{self_regulating_cars}, and coarse bins are also what a human driver can actually follow. For human-in-the-loop deployment, the output is a bounded advisory in the spirit of prior advisory-autonomy work~\cite{Yan_2023,cho2023temporal,fridman2018human}; for automated vehicles, it can be passed to an existing longitudinal controller. In both cases the self-regulation layer nudges the vehicle toward network-friendly behavior without claiming full authority over the car.

\noindent\textbf{Safety and etiquette filter.}
Every advisory passes through a local filter before it is shown or executed. The filter enforces posted speed limits, acceleration and deceleration bounds, minimum front and rear gaps, target-lane time-to-collision margins, a lane-change dwell time, a cap on lane changes per kilometer, and a limit on the braking an advisory may impose on target-lane followers. It also blocks low-speed behavior in uncongested conditions and synchronized all-lane slowdowns unless downstream congestion justifies them. Blocked or modified actions are surfaced through stable diagnostics: safety-masked action, etiquette block, follower-disruption block, and external override. This layer is what allows a network objective to be exposed safely inside mixed human traffic, and it makes the executed action, rather than the raw policy proposal, the quantity that training and evaluation measure.

\noindent\textbf{Degraded operation.}
The edge design follows one rule: stale data is worse than missing data. If GPS goes stale, the observation builder holds the last valid speed for a short window rather than reporting a stop; if no peers are heard, cooperation fields revert to explicit neutral values rather than silent zeros; if a display or logger stalls, the pipeline drops outputs rather than queuing an advisory that no longer matches the scene. These modes do not make the system complete, but they turn common in-car failures into explicit states rather than hidden dependencies.

\noindent\textbf{Deployment tiers.}
The same architecture admits three hardware realizations that differ only in which observation fields are measured rather than neutral, a difference the provenance map makes legible to the policy. \emph{Tier 0} is an app: a modern phone already carries the GPS, inertial sensing, and compute for the observation builder and a two-layer policy, with the camera optional. The advisory rail for this tier operates at scale today; mobile telematics platforms such as CMT and Samsara deliver real-time, cloud-assisted driving feedback through phone apps and lightweight tags, with CMT alone measuring tens of millions of drivers daily~\cite{cmt2025,samsara2025}. The predecessor argued that this makes lightweight, app-level integration a credible path from learned speed modulation to system-level coordination without infrastructure changes~\cite{self_regulating_cars}; our design inherits that path and removes its remaining runtime dependency, shrinking the cloud's role to training, model updates, and offline analytics. \emph{Tier 1} is a retrofit kit, the prototype of Section~\ref{sec:eval}: a windshield camera, a USB GPS receiver, an optional OBD-II dongle as the preferred ego-speed source, an embedded board whose developer kit retails for roughly \$250~\cite{nvidia2023jetson}, and any display. \emph{Tier 2} is native: a vehicle with automated longitudinal control takes the filtered advisory as a set-point for its existing controller. A fleet can mix tiers freely, which makes the 25-vehicle deployment of Section~\ref{sec:vision} an operational decision rather than a hardware program.
