\section{Related Work}
\label{sec:related}

\noindent\textbf{Sparse AVs as traffic actuators.}
Stern et al. showed that a single controlled vehicle can damp stop-and-go waves on a ring track~\cite{stern2018dissipation}, establishing the sparse-actuator premise. Flow and related mixed-autonomy RL work show that learned controllers can improve simulated traffic at low AV penetration~\cite{wu2017flow,vinitsky2018benchmarks,kreidieh2018dissipating}. CIRCLES/MegaVanderTest is the strongest field evidence that controlled vehicles can affect open-road traffic, but it uses purpose-built controlled vehicles and a centralized speed planner that assigns targets over cellular connectivity~\cite{lee2024traffic}. Our focus is different: a vehicle-native, edge-executed design whose runtime communication is aggregate state rather than command dispatch.

\noindent\textbf{Connected-vehicle messaging.}
Deployed connected-vehicle standards have each car broadcast its own position, speed, heading, and path history for collision avoidance, at up to ten hertz: the SAE J2735 Basic Safety Message (BSM) over DSRC and the ETSI Cooperative Awareness Message (CAM) over C-V2X~\cite{sae2020j2735,etsi2019cam,kenney2011dedicated}. (J2735 is a message-set dictionary that also defines aggregate probe-data and traveler-information messages; the widely deployed safety broadcast is the per-vehicle BSM.) These are per-vehicle and sender-centered, so a receiver that wants a density or queue estimate must track and fuse many senders, reintroducing the per-vehicle identity, linkage, and fusion cost the broadcast was meant to avoid. Within the same ETSI family, the Collective Perception Service shares perception rather than only ego state, broadcasting lists of detected objects~\cite{etsi2023cpm}; but the unit is still a per-object record that must be fused and de-duplicated, it carries object positions, and its size grows with scene complexity. Probe-vehicle and floating-car-data systems do compute neighborhood traffic state such as density and mean speed~\cite{seo2017traffic,herrera2010evaluation}, but by uplinking per-vehicle traces to a backend that aggregates centrally, which is precisely the cloud coordinator our design removes. Our contract takes the complementary position on the same axis: the unit of exchange is a fixed-size, receiver-side neighborhood aggregate, computed over whoever is currently in range, with no sender addressed, retained beyond the freshness window, or reconstructable, and with no per-object record and no backend in the loop. Because it is built from onboard perception as well as received summaries, it naturally covers non-AV (human-driven) vehicles too, and it reports whether local flow is approaching a bad operating region rather than the position of any individual car. The physical radio can be the same DSRC or C-V2X link; only the message semantics differ.

\noindent\textbf{Infrastructure-centric traffic control.}
Ramp metering, variable speed limits, adaptive signal control, and freeway management systems remain the dominant deployed tools~\cite{arnold1998ramp,papageorgiou2002freeway,scats,scoot}. They are powerful where sensors and actuators exist, but they depend on fixed infrastructure and centralized operational visibility. Self-regulating cars instead treat vehicles as mobile actuators that can be introduced incrementally.

\noindent\textbf{Advisory systems.}
Human-compatible advisory systems show how network objectives can be translated into driver-facing recommendations~\cite{Yan_2023,cho2023temporal,fridman2018human}. This matters because early deployment will be mixed: some vehicles may be automated, some may show dashboard advisories, and many will ignore the system. The open systems question is therefore not only control optimality, but compliance, incentives, and fairness under partial adoption.

\noindent\textbf{Edge AI and networked sensing.}
Embedded perception models and Jetson-class hardware make on-vehicle traffic-state estimation increasingly practical~\cite{nvidia2023jetson,redmon2016yolo,yang2024depth}. Cloud video analytics demonstrates the value of centralized visual processing but also the cost of moving raw data off the edge~\cite{kang2017noscope,kang2018blazeit}. Our communication model takes the opposite position: infer locally, exchange only semantic aggregate state, and keep safety-critical control on the vehicle.
\vspace{-0.4cm}